Non-Vertical Cultural Transmission, Assortment, \\and the Evolution of Cooperation

### 2021-04-13 ms/main.tex
Added comment about stable and unstable polymorphism

% in gamma
\begin{enumerate}
\item \emph{Fixation of cooperation}: 
	if \emph{(i)} $T_A \ge T_B$ and $c < \gamma_1$; or 
	if \emph{(ii)} $T_A < T_B$ and $v>\hat v$ and $c < \gamma_2$.
\item \emph{Fixation of defection}: 
    if \emph{(iii)} $T_A \ge T_B$ and $\gamma_2 < c$; or 
	if \emph{(iv)} $T_A < T_B$ and $\gamma_1 < c$.
\item \emph{Stable polymorphism (coexistence)}: 
    if \emph{(v)} $T_A < T_B$ and $v<\hat{v}$ and $c < \gamma_1$; or 
    if \emph{(vi)} $T_A < T_B$ and $v>\hat{v}$ and $\gamma_2 < c < \gamma_1$.
\item \emph{Unstable polymorphism (bistable competition)}:
    if \emph{(vii)} $T_A > T_B$ and $\gamma_1 < c < \gamma_2$.
\end{enumerate}

\end{result}
These conditions are illustrated in Figures~\ref{fig:equilibria}a, \ref{fig:equilibria}b, \ref{fig:equilibria_v1}a, and \ref{fig:equilibria_v1}b, and the analysis is in Appendix~\ref{sec:appendixB}.

>>>>

% in gamma
\begin{enumerate}
\item \emph{Fixation of cooperation}: 
	if \emph{(i)} $T_A \ge T_B$ and $c < \gamma_1$; or 
	if \emph{(ii)} $T_A < T_B$ and $v>\hat v$ and $c < \gamma_2$.
\item \emph{Fixation of defection}: 
    if \emph{(iii)} $T_A \ge T_B$ and $\gamma_2 < c$; or 
	if \emph{(iv)} $T_A < T_B$ and $\gamma_1 < c$.
\item \emph{Stable polymorphism}: 
    if \emph{(v)} $T_A < T_B$ and $v<\hat{v}$ and $c < \gamma_1$; or 
    if \emph{(vi)} $T_A < T_B$ and $v>\hat{v}$ and $\gamma_2 < c < \gamma_1$.
\item \emph{Unstable polymorphism}:
    if \emph{(vii)} $T_A > T_B$ and $\gamma_1 < c < \gamma_2$.
\end{enumerate}

\end{result}
These conditions are illustrated in Figures~\ref{fig:equilibria}a, \ref{fig:equilibria}b, \ref{fig:equilibria_v1}a, and \ref{fig:equilibria_v1}b, and the analysis is in Appendix~\ref{sec:appendixB}.
Note that “stable polymorphism” is sometimes called “coexistence” and “unstable polymorphism” is “bistable competition.
